Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-08 sas2015/content/intro.tex
commiting introduction changes

This paper presents an approach to data-flow analysis that avoids a type
of infeasible path that arises in object-oriented programs when two or more
methods are dynamically dispatched on the same receiver object.
%\mtodo{Should we define the term ``receiver''?}
In such cases, if the
method calls are polymorphic (i.e., if they dispatch to different method definitions 
depending on the type of the receiver expression at run time), then their dispatch 
behaviours will be correlated. A recent paper~\cite{DBLP:journals/scp/Tip15} identified
this problem but did not present a concrete solution or algorithm, and we are not aware 
of any existing data-flow analysis that is capable of avoiding infeasible paths that arise 
in the presence of correlated method calls (see Section~\ref{sec:Related} for a discussion
of related work).

>>>>

This paper presents an approach to data-flow analysis that avoids a type
of infeasible path that arises in object-oriented programs when two or more
methods are dynamically dispatched on the same receiver object.
%\mtodo{Should we define the term ``receiver''?}
In such cases, if the
method calls are polymorphic (i.e., if they dispatch to different method definitions 
depending on the type of the receiver expression at run time), then their dispatch 
behaviours will be correlated. A recent paper~\cite{DBLP:journals/scp/Tip15} identified
this problem but did not present a concrete solution or algorithm, and we are not aware 
of any existing data-flow analysis that is capable of avoiding infeasible paths that arise 
in the presence of correlated method calls.
% (see Section~\ref{sec:Related} for a discussion
%of related work).
